\chapter{Acknowledgements}
    
% \begin {center}

% \end{center}

First of all, I wish to acknowledge my parents because they have always supported and encouraged me. 
% They taught me the importance of learning and also the importance of always giving the best possible version of oneself.
I would like to thank Alvaro as well for his support and comprehension during the whole project and for his help and patience in the difficult moments. 
\\

I am particularly grateful for the assistance given by my thesis supervisor, Víctor González Pacheco, for giving me some key pointers without which this project would not have been possible. 
I also would like to thank the teachers I had during my life. Those who were better for helping me to easily acquire the knowledge of their subjects, and those who were worse for aiding me in learning how to overcome difficulties and be self-sufficient. 
\\

And, finally, I would like to thank my friends and family, specially Rocío and Blanca, for always being there for me. 


\begingroup
\let\clearpage\relax
\chapter{Agradecimientos}
\endgroup
Lo primero querría dar las gracias a mis padres, por el apoyo y el ánimo que me dan siempre. 
También me gustaría agradecer a Álvaro su apoyo, comprensión y paciencia durante el proyecto y su ayuda en los momentos más difíciles. 
\\

La ayuda de mi tutor, Víctor González Pacheco, ha sido muy importante, principalmente algunas indicaciones que han hecho posible la realización de este proyecto. 
Me gustaría reconocer también la ayuda de todos los profesores que he tenido en mi vida de estudiante. 
Aquellos que eran mejores, por ayudarme a adquirir fácilmente los conocimientos y aquellos que eran peores por ayudarme a aprender cómo superar dificultades y llegar a ser capaz de aprender autónomamente. 
\\

Finalmente, me gustaría dar las gracias a mis amigos y familia, especialmente a Rocío y a Blanca, por estar siempre ahí cuando les necesito. 